Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-23 writing/embedded_meta_learning_main.tex
More comments/clarity

\paragraph{Basic meta-learning:} To perform a basic task, first, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. These examples are fed to $\mathcal{M}$ to produce a function embedding. This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end on targets for the second dataset. (Having two distinct datasets forces generalization at the meta-learning level). See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 

@@

\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results} (with good sample-efficiency, see supp. fig. \ref{supp_poly_sweep_results}). \par 

@@

\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig. \ref{poly_meta_map_results}. We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on. The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction. However, it performs better from examples than language, which is not completely surprising, since the examples provide a richer cue to the task. \par 

@@

\paragraph{Basic meta learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig. \ref{cards_basic_results}. We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game. In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case. Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks. Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}. \par

@@

\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior. For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training. In Fig. \ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it. This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out). Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so the results are quite good. \par

>>>>

\paragraph{Basic meta-learning:} To perform a basic task, first, a training dataset is encoded by $\mathcal{I}$ and $\mathcal{T}$. These examples are fed to $\mathcal{M}$ to produce a function embedding. This function embedding is mapped through $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a (possibly distinct) dataset of embedded inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end on targets for the second dataset. (Having two distinct datasets forces generalization at the meta-learning level, see appendix 
ref{app_clarifying_holdouts}.) See appendix \ref{app_model_details} for detailed architecture, operation, and hyper-parameters. \par 

@@

\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in Fig. \ref{poly_basic_results} (with good sample-efficiency, see supp. fig. \ref{supp_poly_sweep_results}). \par 

@@

\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig. \ref{poly_meta_map_results}. We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on. The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction. However, it performs better from examples than language, which is not completely surprising, since the examples provide a richer cue to the task. \par 

@@

\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of playing a held-out game from examples in Fig. \ref{cards_basic_results}. We compare two different possible hold-out sets: 1) train on half the tasks at random, or 2) specifically hold out all the ``losers'' variations of the ``straight flush'' game. In either of these cases, the meta-learning system achieves well above chance performance (0) at the held out tasks, although it is slightly worse at generalizing to the targeted hold out, despite having more training tasks in that case. Note that the sample complexity in terms of number of trained tasks is not that high, even training on 20 randomly selected tasks leads to good generalization to the held-out tasks. Furthermore, the task embeddings generated by the system are organized by the features of the games, see appendix \ref{app_cards_tsne}. \par

@@

\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior. For example, if the system is trained to map games to their losers variations, it can generalize this mapping to a game it has not been trained to map, even if the source or target of that mapping is held out from training. In Fig. \ref{cards_meta_map_results}) we demonstrate this by taking the mapped embedding and evaluating the reward received by playing the targeted game with it. This task is more difficult than simply learning to play a held out game from examples, because the system will actually receive no examples of the target game (when it is held out). Furthermore, in the case of the losers mapping, leaving the strategy unchanged would produce a large negative reward, and chance performance would produce 0 reward, so the results are quite good. \par
